---
title: "Analysis of Covariance Assignment Question"
author: "Haiyang Jiang (Jason) & Sichen Liu (Coco)"
date: '2018-11-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this assignment, we will look at the sexab dataset. The response variable is 'ptsd' and the independent variables are 'csa' (as a factor) and 'cpa' (as a covariate). We will go through the Analysis of Covariance step by step.

Setup in R:
```{r}
library(car)
library(ggplot2)
library(multcomp)
library(faraway)
data(sexab,package='faraway')
# If you would like to know the details about this dataset
?sexab
```

a. We first would like to plot 'cpa' vs 'ptsd' for both levels of 'csa' seperately. Fill in the blanks for the following code.
```{r}
ggplot(aes(x = , y = ),data=) +
  geom_point() + 
  facet_wrap(~ )
```

b. Build an ANOVA model for 'ptsd' vs 'csa', and a linear model for 'ptsd' vs 'cpa'. Check if the normality and equal variance assumptions are met for these two models. If not, perform an appropriate transformation.
```{r}

```


c. Check if the assumption of homogeneity of regression slopes is met through an ANOVA test.
```{r}
full_mod <- aov( ~  * , data=)
anova(full_mod)
```


d. As mentioned, we can use ggplot to visualize if the regression lines are parallel. Please fill in the blanks for the following code:
```{r}
ggplot(, aes(x=, y=, color=, shape=)) +
  geom_point() + 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE) +
  labs(x = "") + 
  labs(y = "") + 
  labs(title = "Scatterplot of sexab Data with fitted regression lines")
```


e. Build the model and perform an ANCOVA test. Conclude on your findings.
```{r}
red_mod <- aov( ~ ., data=)
Anova(red_mod,type='2')
```



